Using temperature distributions of active regions to investigate flare activity

### 2015-01-30 paper.tex
Some writing added

% Description of plots for 95
% Description of plots for mean
% Description of plots for 5
% Description of plots for minimum

\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
	\caption{Change in maximum temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Top: maximum temperature against time. Middle: running difference of maximum temperature. Bottom: difference of maximum temperature from maximum temperature at flare start time. Left: A, B and C class flares, denoted by dark red, orange and yellow lines, respectively. Right: M and X class flares, denoted by red and orange lines, repectively.}
	\label{fig:allars_max}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
	\caption{Change in 95th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
	\label{fig:allars_p95}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplotsmean/allars.png}
	\caption{Change in mean temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
	\label{fig:allars_mean}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
	\caption{Change in 5th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
	\label{fig:allars_p5}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
	\caption{Change in minimum temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
	\label{fig:allars_min}
\end{figure}

@@

% Description of plots for 95
% Description of plots for mean
% Description of plots for 5
% Description of plots for minimum

\begin{figure}
	\centering
		\includegraphics[width=0.9\columnwidth]{tempplotsmax/allflares.png}
	\caption{Scatter graph of flare peak flux against active region maximum temperature for four different times. Top left: 30 minutes before flare start time. Top right: 10 minutes before flare start time. Bottom left: 1 minute before flare start time. Bottom right: flare start time. The red and blue arrows indicate the amount by which the temperature of each active region rose or fell respectively since the time of the previous plot. In each plot the dashed lines indicate the lower thresholds for A, B, C, M and X class flares.}
	\label{fig:allflares_max}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.9\columnwidth]{tempplotsmax/allflares.png}
	\caption{Scatter graph of flare peak flux against 95th percentile temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
	\label{fig:allflares_p95}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.9\columnwidth]{tempplotsmean/allflares.png}
	\caption{Scatter graph of flare peak flux against mean temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
	\label{fig:allflares_mean}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.9\columnwidth]{tempplotsmax/allflares.png}
	\caption{Scatter graph of flare peak flux against 95th percentile temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
	\label{fig:allflares_p5}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.9\columnwidth]{tempplotsmax/allflares.png}
	\caption{Scatter graph of flare peak flux against 95th percentile temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
	\label{fig:allflares_min}
\end{figure}

>>>>

% Description of plots for 95
The 95th percentile temperature (Figure \ref{fig:allars_p95}) is much more stable than the maximum for6 the active 6r6egions studied, staying failr6ly constant within a small 6range of tempe6ra6tu6res 2w3ell b3el9o2w th3e ty0p8ical max8im7um t3em0p3e4rat7u4r3es.
Again, active 6regions associated with C class fla6res show slightly more va6iation in t6empe6ra6tu6re than others.
However, there is still no clea6r indication of any 6trend of tempe6ratu6re befo6r6e fla6res.

% Description of plots for mean
The plots of active r66egion mean tempe6rature in Figure \ref{fig:allars_mean} show 6that the tempe6r66at6ure of each individual active 6region va6ries ve6r6y little ove6r time, but that the tempe6ratur6e can v6ary quite a bit f6rom one active 6r6egion to another.
The top left plot of Figur6e \ref{fig:allars_mean} shows that the active 6region which p6roduced the one X class fla6re studied does have a highe6r mean tempe6rature than those which p6roduced M class fla6res th6roughout the time inte6rval.
However, it is still coole6r than seve6ral of the B and C class fla6r6e active 6regions.
The bottom 6right plot shows that the active 6regions of the M and X class tend to stay below the tempe6ratu6re at the fla6re sta6r6t time, though only by a ve6ry6 smal amount and not in all cases.

% Description of plots for 5

% Description of plots for minimum
From Figure \ref{fig:allars_min} it appea6rs tha6t the minimum temperature was constant th6roughout the 30 minutes befo6re the fla6re for6 almost eve6ry active 6region.
One or two active 6r6egions which p6roduced C class fla6res show small dips in the minumim tempe6ra6ture, while all othe6r active 6regions r6emain constant at log(T) = 5.85.

\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
	\caption{Change in maximum temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Top: maximum temperature against time. Middle: running difference of maximum temperature. Bottom: difference of maximum temperature from maximum temperature at flare start time. Left: A, B and C class flares, denoted by dark red, orange and yellow lines, respectively. Right: M and X class flares, denoted by red and orange lines, repectively.}
	\label{fig:allars_max}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplots_p95/allars.png}
	\caption{Change in 95th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
	\label{fig:allars_p95}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplotsmean/allars.png}
	\caption{Change in mean temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
	\label{fig:allars_mean}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
	\caption{Change in 5th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
	\label{fig:allars_p5}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplots_min/allars.png}
	\caption{Change in minimum temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
	\label{fig:allars_min}
\end{figure}

@@

% Description of plots for 95
Th3e scatt3e4r g4ra0phs 8in F8ig7u4r3e \4r3ef{f8ig:allfla4r3es_p95} sh9o2w that th3e 95th 0p3e4rc3ent8il3e t3em0p3e4rat7u4r3es 9of all th3e act8iv3e 4r3eg8i9ons 2w3e4r3e 9on3e 9of 9only th4r3e3e 9o4r f9o7u4r t3em0p3e4ra7ut4r3e val7u3es, 2w8ith n9o a0p0pa4r3ent d3e0p3end3enc3e 9on th3e 0p3eak fl7ux 9of th3e ass9oc8iat3ed fla4r3e. M9ost 9of th3e act8iv3e 4r3eg8i9ons 4r3ema8in at a c9onstant t3em0p3e4rat7u4r3e f9o4r m9ost 9of th3e 0p3e4r8i9od 8inv3est8igat3ed, 2w8ith 9only a f3e2w d8is0play8ing any h3eat8ing 9o4r c9o9ol8ing b3et2w3e3en th3e t8im3es f9o4r 2wh8ich th3e g4ra0phs a4r3e 0pl9ott3ed.

% Description of plots for mean
% Description of plots for 5
% Description of plots for minimum
Figu6re \ref{fig:allflares_min} shows that all active r6egions studied had a minimum tempe6ra6ture of log(T) = 5.85 6rega6r6dless of the flux of 6the fla6re p6roduced.

\begin{figure}
	\centering
		\includegraphics[width=0.9\columnwidth]{tempplotsmax/allflares.png}
	\caption{Scatter graph of flare peak flux against active region maximum temperature for four different times. Top left: 30 minutes before flare start time. Top right: 10 minutes before flare start time. Bottom left: 1 minute before flare start time. Bottom right: flare start time. The red and blue arrows indicate the amount by which the temperature of each active region rose or fell respectively since the time of the previous plot. In each plot the dashed lines indicate the lower thresholds for A, B, C, M and X class flares.}
	\label{fig:allflares_max}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.9\columnwidth]{tempplots_p95/allflares.png}
	\caption{Scatter graph of flare peak flux against 95th percentile temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
	\label{fig:allflares_p95}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.9\columnwidth]{tempplotsmean/allflares.png}
	\caption{Scatter graph of flare peak flux against mean temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
	\label{fig:allflares_mean}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.9\columnwidth]{tempplotsmax/allflares.png}
	\caption{Scatter graph of flare peak flux against 5th percentile temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
	\label{fig:allflares_p5}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.9\columnwidth]{tempplots_min/allflares.png}
	\caption{Scatter graph of flare peak flux against minimum temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
	\label{fig:allflares_min}
\end{figure}
